Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/abstract.tex

We considered engines from four major players in our
experiments--Apple, Google, Microsoft, and Mozilla. Our results
indicate that both techniques revealed several bugs, many of which
confirmed by developers. We reported \noBugsTransplantation{} bugs
with test transplantation (with \noBugsTransplantationConfirmed{} bugs
confirmed and \noBugsTransplantationFixed{} fixed) and reported
\noBugsDifferentialTesting{} bugs with differential testing
(with \noBugsDifferentialTestingConfirmed{} confirmed
and \noBugsDifferentialTestingFixed{} fixed). Furthermore, results
indicate that most of these bugs affected two engines--Apple's
\jsc{} (\percJSC{}) and Microsoft's \chakra{} (\percChakra{}); we found
only \Fix{one} bug in Google \veight{} and none in Mozilla's
\smonkey{}. Although more research needs to be done to optimizie 
warning triaging, our results show that exploring diversity is a
valuable help to find bugs in JavaScript engines.

>>>>

We considered engines from four major players in our
experiments--Apple, Google, Microsoft, and Mozilla. Our results
indicate that both techniques revealed several bugs, many of which
confirmed by developers. We reported \noBugsTransplantation{} bugs
with test transplantation (\noBugsTransplantationConfirmed{} of these bugs
confirmed and \noBugsTransplantationFixed{} fixed) and reported
\noBugsDifferentialTesting{} bugs with differential testing
(\noBugsDifferentialTestingConfirmed{} of these confirmed
and \noBugsDifferentialTestingFixed{} fixed). Results indicate that
most of these bugs affected two engines--Apple's
\jsc{} and Microsoft's \chakra{}. To sum, our results show that
exploring diversity is effective to find bugs in JavaScript engines.

%% Although more research needs to be done to optimizie 
%% warning triaging,

%% ; we found
%% only \Fix{one} bug in Google \veight{} and none in Mozilla's
%% \smonkey{}

### 2018-08-25 paper/paper.tex

\begin{table}[t!]
  \setlength{\tabcolsep}{4pt}    
  \centering
  \caption{\label{fig:falsepositives}\label{fig:truepositives}\label{fig:piecharts-transplantation}Distribution of false and true positives.}
  \begin{tabular}{ccr}
    \toprule
    & source &  \#\\
    \midrule
    \multirow{5}{*}{False Positives} & Undefined Behavior & 313 \\
    & Timeout/OME & 15 \\
    & Not Implemented & 22 \\
    & Non-Standard Element & 177 \\
    & Unknown & 135 \\
    \midrule
    \multirow{2}{*}{True Positives} & Duplicate & 10 \\
    & Bug & 24 \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\begin{table}[t!]
  \setlength{\tabcolsep}{4pt}    
  \centering
  \caption{\label{fig:falsepositives}\label{fig:truepositives}\label{fig:piecharts-transplantation}Distribution of false and true positives.}
  \begin{tabular}{ccr}
    \toprule
    & source &  \#\\
    \midrule
    \multirow{5}{*}{False Positives} & Undefined Behavior & 252 \\
    & Timeout/OME & 15 \\
    & Not Implemented & 22 \\
    & Non-Standard Element & 119 \\
    & Unknown & 135 \\
    \midrule
    \multirow{2}{*}{True Positives} & Duplicate & 10 \\
    & Bug & 24 \\
    \bottomrule
  \end{tabular}
\end{table}
